Traffic aware Precoding and Resource Allocation schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} systems

### 2014-09-29 Report/problem_formulation_intro.tex
Antti Changes included

For practical and tractability reasons, we may impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total backlogged packets available at the transmitter. As a result, the number of backlogged packets \me{v_k} remaining in the system for the user \me{k} is given by
\begin{equation} \label{rate_constraint_a}
v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0
\end{equation}
The above positivity constraint need to be satisfied by \me{v_k} to avoid the excessive allocation of the resources.

Before proceeding further, we note that the constraint in \eqref{rate_constraint_a} is handled implicitly by the definition of the \me{\ell_q} in the objective of \eqref{eqn-3}. As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}. Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}. Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained. The choice of the norm \me{\ell_q} used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as
\begin{itemize}
\item With \me{\ell_{q = 1}}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions. As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
\item With \me{\ell_{q = 2}}, the objective prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets. For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
\item With \(\ell_{q = \infty} \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
\end{itemize}

>>>>

For practical reasons, we may impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total backlogged packets available at the transmitter. As a result, the number of backlogged packets \me{v_k} remaining in the system for the user \me{k} is given by
\begin{equation} \label{rate_constraint_a}
v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0
\end{equation}
The above positivity constraint need to be satisfied by \me{v_k} to avoid the excessive allocation of the resources.

Before proceeding further, we note that the constraint in \eqref{rate_constraint_a} is handled implicitly by the definition of the \me{\ell_q} in the objective of \eqref{eqn-3}. As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}. Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}. Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained. The choice of the norm \me{\ell_q} used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as
\begin{itemize}
\item With \me{\ell_{q = 1}}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions. As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem when the queue size is large enough for all users.
\item With \me{\ell_{q = 2}}, the objective prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets. For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the number of backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
\item With \(\ell_{q = \infty} \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
\end{itemize}

### 2014-09-29 Report/simulation_distributed.tex
Antti Changes included

The performance of the distributed algorithms are studied in this section by comparing with the centralized algorithms. The performance is compared using the total number of backlogged packets after each \ac{SCA} update points. Fig. \ref{fig-d-1} compares the performance of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}. Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}. As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the choice of the step size used in the subgradient update. Since the interference values are fixed for local subproblem in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update using \eqref{primal-sg-update} is not valid.

The Fig. \ref{fig-d-1} plots the performance of the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} points. In between the \ac{SCA} updates, the primal or the \ac{ADMM} schemes are performed for \me{J_{\max} = 20} iterations by exchanging either the fixed interference variables in the primal approach or the dual variables in the \ac{ADMM} scheme. It can be seen from Fig. \ref{fig-d-1} that the distributed algorithms approaches the centralized performance by exchanging minimal information between the coordinating \acp{BS}.
\begin{figure*}
\centering
\subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-3}
\label{fig-d-1}
}
\hfill
\subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-5}
\label{fig-d-2}
}
\caption{Number of backlogged packets at each \ac{SCA} points}
\label{fig-d}
\end{figure*}

@@

Fig. \ref{fig-d-2} plots the performance of the centralized and the distributed algorithms at each \ac{SCA} update. In case of the distributed algorithms, in between each \ac{SCA} update, the primal or the \ac{ADMM} exchanges are performed for \me{J_{\max} = 20} iterations. In practice, \me{J_{\max} = 1} can be set to perform the \ac{SCA} update, \ac{ADMM} or primal update, and the receive beamformers \me{\mvec{W}{k,n}} update at the same instant. The data tips are used to highlight the convergent points of various algorithms. The performance of the \ac{JSFRA} schemes using the primal decomposition are notably inferior compared to the \ac{ADMM} approach for the same schemes. It is mainly attributed to the difficulty in selecting the step size for the system employing \me{N_B \geq 3} \acp{BS}.
% \begin{figure*}
% \centering
% \begin{subfigure}{0.49\textwidth}
% \includegraphics[width=\textwidth]{fig-5}
% \caption{Queue deviation}
% \end{subfigure}
% \hfill
% \begin{subfigure}{0.49\textwidth}
% \includegraphics[width=\textwidth]{fig-6}
% \caption{Sum rate performance}
% \end{subfigure}
% \caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace} model}
% \label{fig-d-2}
% \end{figure*}

Fig. \ref{fig-d-3.1} compares the performances of the centralized algorithm based on the \ac{MSE} reformulation with the iterative approach proposed in Section \ref{sec-4.3} based on solving the \ac{KKT} conditions. In Fig. \ref{fig-d-3.1}, the plots are compared by the surplus number of backlogged packets at the end of each iteration or the \ac{SCA} update point. Fig. \ref{fig-d-3.1} shows that the \me{\ell_1} norm for \ac{JSFRA} scheme provides better performance over rest of the schemes due to its greedy objective. The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}, thereby performs the worst of all other approaches. The heuristic method used in the figure is obtained by forcing the dual variable \me{\sigma_{l,k,n}} in \eqref{kkt-mse-4.2} to \me{0} when the queue deviation is negative \me{Q_k - t_k < 0}, if not, then it will be the same as in \eqref{kkt-mse-4.2}. The additional condition can be justified due to the dropping of absolute value operator from the objective. It can be seen that the heuristic method oscillates near the optimal point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{fig-9-2}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace} model}
\label{fig-d-3.1}
\end{figure}

The objective values are mentioned in the legend for all the schemes, since the objective of \me{\ell_2} norm is not the same as \me{\ell_1} norm, which is used for the plot. The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} based approach achieves nearly the same objective value of \me{6.62} but different \me{\chi}, since the dual variables \me{\alpha_{l,k,n}} and \me{\sigma_{l,k,n}} are not iterated until convergence between each \ac{SCA} steps in the \ac{KKT} approach. In the simulation, we update all the variables at each iteration due to the practical issues in the signaling between the \acp{BS}. Fig. \ref{fig-d-3.1} also compares the effect of dropping the squared rate variable from the objective in the \ac{Q-WSRME} scheme compared to the \me{\ell_2} norm which includes it. By dropping the squared rate variable, the \ac{Q-WSRME} scheme minimizes the number of queued packets in a prioritized manner based on the respective queues. On contrary, the \me{\ell_2} norm allocate rates to the users with the higher number of queued packets before addressing the users with the smaller number of queued packets.

>>>>

The performance of the distributed algorithms are studied in this section by comparing with the centralized algorithms. The performance is compared using the total number of backlogged packets after each \ac{SCA} update points. Fig. \ref{fig-d-1} compares the performance of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}. Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}. The total number of queued packets assumed for both figures is given by \me{Q_k = [5,7,9,11,8,12,5,4]} bits. As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the choice of the step size used in the subgradient update. Since the interference values are fixed for local subproblem in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.

The Fig. \ref{fig-d-1} plots the performance of the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} points. In between the \ac{SCA} updates, the primal or the \ac{ADMM} schemes are performed for \me{J_{\max} = 20} iterations to exchange either the fixed interference variables in the primal approach or the dual variables in the \ac{ADMM} scheme. In Fig. \ref{fig-d}, the total number of backlogged packets at each \ac{SCA} points are plotted without the inner loop iterations of \me{J_{\max}} times for the primal or the dual variables convergence. It can be seen from Fig. \ref{fig-d-1} that the distributed algorithms approaches the centralized performance by exchanging minimal information between the coordinating \acp{BS}.
\begin{figure*}
\centering
\subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-3-1}
\label{fig-d-1}
}
\hfill
\subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-5-1}
\label{fig-d-2}
}
\caption{Number of backlogged packets at each \ac{SCA} points}
\label{fig-d}
\end{figure*}

@@

Fig. \ref{fig-d-2} plots the performance of the centralized and the distributed algorithms at each \ac{SCA} update. In case of the distributed approaches, in between each \ac{SCA} update, the primal or the \ac{ADMM} exchanges are performed for \me{J_{\max} = 20} iterations. In practice, \me{J_{\max} = 1} can be set to perform the \ac{SCA} update, \ac{ADMM} or primal update, and the receive beamformers \me{\mvec{W}{k,n}} update at the same instant, which affects the convergence rate and the stationary point of the final solution. The data tips are used to highlight the convergent points of various algorithms. The performance of the \ac{JSFRA} schemes using the primal decomposition are notably inferior compared to the \ac{ADMM} approach for the same schemes. It is mainly attributed to the difficulty in selecting the step size for the system employing \me{N_B \geq 3} \acp{BS}.
% \begin{figure*}
% \centering
% \begin{subfigure}{0.49\textwidth}
% \includegraphics[width=\textwidth]{fig-5}
% \caption{Queue deviation}
% \end{subfigure}
% \hfill
% \begin{subfigure}{0.49\textwidth}
% \includegraphics[width=\textwidth]{fig-6}
% \caption{Sum rate performance}
% \end{subfigure}
% \caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace} model}
% \label{fig-d-2}
% \end{figure*}

Fig. \ref{fig-d-3.1} compares the performances of the centralized algorithm based on the \ac{MSE} reformulation with the iterative approach proposed in Section \ref{sec-4.3} based on solving the \ac{KKT} conditions. In Fig. \ref{fig-d-3.1}, the plots are compared by the surplus number of backlogged packets at the end of each iteration or the \ac{SCA} update point. Fig. \ref{fig-d-3.1} shows that the \me{\ell_1} norm for \ac{JSFRA} scheme provides better performance over rest of the schemes due to its greedy objective. The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}, thereby performs the worst of all other approaches. The heuristic method used in the figure is obtained by forcing the dual variable \me{\sigma_{l,k,n}} in \eqref{kkt-mse-4.2} to \me{0} when the queue deviation is negative \me{Q_k - t_k < 0}, if not, then it will be the same as in \eqref{kkt-mse-4.2}. The additional condition can be justified due to the dropping of absolute value operator from the objective. It can be seen that the heuristic method oscillates near the optimal point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{fig-9-2-1}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace} model}
\label{fig-d-3.1}
\end{figure}

The objective values are mentioned in the legend for all the schemes, since the objective of \me{\ell_2} norm is not the same as \me{\ell_1} norm, which is used for the plot. The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} based approach achieves nearly the same objective value of \me{6.62} but different \me{\chi}, since the dual variables \me{\alpha_{l,k,n}} and \me{\sigma_{l,k,n}} are not iterated until convergence between each \ac{SCA} steps in the \ac{KKT} approach. In the simulation, we update all the variables at once at each iteration, \textit{i.e}, \me{J_{\max} = 1}, which is well justified for the practical implementations due to the signaling overheads. Fig. \ref{fig-d-3.1} also compares the effect of dropping the squared rate variable from the objective in the \ac{Q-WSRME} scheme compared to the \me{\ell_2} norm which includes it. By dropping the squared rate variable, the \ac{Q-WSRME} scheme minimizes the number of queued packets in a prioritized manner based on the respective queues. On contrary, the \me{\ell_2} norm allocate rates to the users with the higher number of queued packets before addressing the users with the smaller number of queued packets.

### 2014-09-29 Report/simulation_results.tex
Antti Changes included

In this section, we discuss the performance of the centralized algorithms from Section \ref{sec-3} for a few system configurations. To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources. The number of packets waiting at the transmitter for each user is given by \me{Q_k = 5,8} and \me{6} bits respectively.

Fig. \ref{tbl-1} plots the sub-channel wise channel seen by the users followed by the assigned rates over each sub-channel by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the band-wise \ac{Q-WSRM} scheme using \ac{WMMSE} precoder design proposed in \cite{wmmse_shi}. The performance metric used for the comparison of different algorithms is the total number of backlogged bits left over at each slot after the allocation, which is denoted by \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}. It can be seen from Fig. \ref{tbl-1}, the \ac{Q-WSRME} scheme provides more priority to the third user with \me{Q_{3} = 6} bits as compared to the first user with \me{Q_{1} = 5} bits while allocating the first sub-channel. In contrast to the \ac{Q-WSRME} scheme, the \ac{JSFRA} approach assigns the first user on the first sub-channel thereby reducing the total number of backlogged packets waiting at the transmitter.
\begin{table*}
\centering
\renewcommand{\arraystretch}{1.25} \scriptsize
\begin{tabular}{|*{14}{c|}}
\hline
\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRME approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \emph{backpreassure})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
\cline{3-14}
 && Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} \\
\hline
\me{1} & \me{5} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.91} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.46}  &  \me{3.54} & \me{0} &  \me{4.36}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
\me{3} & \me{6} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{5.72} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{5.79} & \me{5.81} &  \me{0}  &  \me{0} \\
\hline
\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{5.28} bits} & \multicolumn{3}{c|}{\me{3.91} bits} & \multicolumn{3}{c|}{\me{5.28} bits} \\
\hline
\end{tabular}
\caption{Sub channel wise allocation for a scheduling instant}
\label{tbl-1}
\end{table*}
%\begin{figure}
%\centering
%\includegraphics[width=\columnwidth]{tbl-1}
%\caption{Allocation for a \ac{SISO} Model comparing different Algorithms}
%\label{tbl-1}
%\end{figure}

In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with lowest path loss component. Fig. \ref{fig-1} shows the performance of the centralized schemes for a single receive antenna system. It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRME} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
\begin{figure*}
\centering
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-1-3}
\label{fig-1}}
\hfill
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-2-4}
\label{fig-2}}
\caption{Number of backlogged packets at the \ac{SCA} update points}
\label{fig-a}
\end{figure*}

Fig. \ref{fig-a} compares the performance of the centralized algorithms with the total number of residual bits remaining in the system after the current transmission slot. The reduction in the number of queued packets after each \ac{SCA} updates are plotted in the figures. It can be seen from Fig. \ref{fig-a}, the \ac{Q-WSRM} algorithm is not optimal due to the problem of over allocation when the number of queued packets are small. In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over allocation problem. It can be seen that the \ac{JSFRA} algorithms converge to the optimal point for all formulations proposed in Section \ref{sec-3.2.1}. It can be seen that all the algorithms are Pareto-optimal and provides different performance based on the weights used to find a point in the rate region.

>>>>

In this section, we discuss the performance of the centralized algorithms from Section \ref{sec-3} for a few system configurations. To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources. The number of packets waiting at the transmitter for each user is given by \me{Q_k = 4,8} and \me{4} bits respectively.

Table. \ref{tbl-1} outlines the channel seen by the users over each sub-channel followed by the rates assigned by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the band-wise \ac{Q-WSRM} scheme using \ac{WMMSE} design \cite{wmmse_shi}. The performance metric used for the comparison is the total number of backlogged bits left over at each slot after the allocation, which is denoted by \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}. Even though \me{\mc{U}(1)} and \me{\mc{U}(3)} has equal number of backlogged packets of \me{Q_{1} = Q_{3} = 4} bits, user \me{\mc{U}(3)} got scheduled in the first sub-channel due to the better channel condition. In contrast to the \ac{Q-WSRME} scheme, the \ac{JSFRA} approach assigns the first user on the first sub-channel, which reduces the total number of backlogged packets waiting at the transmitter. The rate allocated for \me{\mc{U}(2)} on the second sub-channel is higher in \ac{JSFRA} scheme compared to the other schemes. It is due to the efficient allocation of the total power shared across the sub-channels.
\begin{table*}
\centering
\renewcommand{\arraystretch}{1.25} \scriptsize
\begin{tabular}{|*{14}{c|}}
\hline
\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRME approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \emph{backpreassure})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
\cline{3-14}
 && SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} \\
\hline
\me{1} & \me{4} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.88}  &  \me{3.11} & \me{0} &  \me{5.49}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
\me{3} & \me{4} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{4.0} & \me{5.81} &  \me{0}  &  \me{0} \\
\hline
\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{3.92} bits} & \multicolumn{3}{c|}{\me{2.51} bits} & \multicolumn{3}{c|}{\me{5.89} bits} \\
\hline
\end{tabular}
\caption{Sub channel wise allocation for a scheduling instant}
\label{tbl-1}
\end{table*}
%\begin{figure}
%\centering
%\includegraphics[width=\columnwidth]{tbl-1}
%\caption{Allocation for a \ac{SISO} Model comparing different Algorithms}
%\label{tbl-1}
%\end{figure}

In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with lowest path loss component. Fig. \ref{fig-1} shows the performance of the centralized schemes for a single receive antenna system. It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRME} schemes to perform the optimal allocations to minimize the total number of backlogged packets. The total number of queued packets for Fig. \ref{fig-1} is given by \me{Q_k = [14,15,14,8,12,9,12,11,11]} bits and for Fig. \ref{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.
\begin{figure*}
\centering
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-1-3-1}
\label{fig-1}}
\hfill
\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
\includegraphics[width=0.48\textwidth]{fig-2-4-1}
\label{fig-2}}
\caption{Number of backlogged packets at the \ac{SCA} update points}
\label{fig-a}
\end{figure*}

The performance of the centralized algorithms are compared by the total number of residual bits remaining in the system after each \ac{SCA} update in Fig. \ref{fig-a}. The \ac{Q-WSRM} algorithm is not optimal due to the problem of over allocation when the number of queued packets are small, as in Fig. \ref{fig-a}. In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over allocation problem. It can be seen that the \ac{JSFRA} algorithms converge to the optimal point for all formulations proposed in Section \ref{sec-3.2.1}. It can be seen that all the algorithms are Pareto-optimal and provides different performance based on the weights used to find a point in the rate region.
